---
output: rmarkdown::github_document
---

# ropendata

Query and Download 'Rapid7' Cybersecurity Data Sets

## Description

'Rapid7' collects cybersecurity data and makes it available via their 'Open Data' <https://opendata.rapid7.com> portal which has an 'API'. Tools are provided to assist in querying for available data sets and downloading any data set authorized to a registered account.
    
## What's Inside The Tin

The following functions are implemented:

- `get_file_details`:	Retrieve details for a given file from a specific Rapid7 Open Data study
- `get_study_details`:	Retrieve details for a specific Rapid7 Open Data study
- `list_studies`:	List available Rapid7 Cybersecurity Studies
- `rapid7_api_key`:	Get or set `RAPID7_OPENDATA_API_KEY` value

## Installation

```{r eval=FALSE}
devtools::install_github("brudis-47/ropendata")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(ropendata)
library(tidyverse)

# current verison
packageVersion("ropendata")

```

### List Studies

```{r message=FALSE, warning=FALSE, error=FALSE}
list_studies()
```

### Get Study Details

```{r message=FALSE, warning=FALSE, error=FALSE}
get_study_details("sonar.national_exposure")
```

### Get Details About A Single Study File

```{r message=FALSE, warning=FALSE, error=FALSE}
get_file_details("sonar.fdns_v2", "2018-06-15-1529049662-fdns_aaaa.json.gz")
```
